---
title: "Your Caculated PGS"
root.dir: "/Dedicated/jmichaelson-wdata/msmuhammad/scratch/PGS/src"
author: "Muhammad Elsadany"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.align='center')
rm(list = ls())
gc()
source("/Dedicated/jmichaelson-wdata/msmuhammad/msmuhammad-source.R")
theme_set(theme_minimal())
formatted_tbl <- function(x) {
  kableExtra::kable_styling(knitr::kable(x))
}
library(plotly)
project.dir <- "/Dedicated/jmichaelson-wdata/msmuhammad/scratch/PGS"
setwd(project.dir)
knitr::opts_knit$set(root.dir = project.dir)
```



```{r pgs combining}
pgs.dir <- "/Dedicated/jmichaelson-wdata/msmuhammad/scratch/PGS/data/derivatives/pgs"
pgs.ls <- data.frame(f = list.files(pgs.dir)) %>%
  mutate(PGS = sub(".rds", "", f)) %>%
  mutate(PGS = sub(".txt", "", PGS))
pcs <- read_table("/Dedicated/jmichaelson-wdata/msmuhammad/scratch/PGS/data/derivatives/gcta_pc20_raw.eigenvec",
                  col_names = c("IID", "FID", paste0("PC", 1:20)))
registerDoMC(cores = 4)
pgs.all <- foreach(i=1:nrow(pgs.ls), .combine = rbind) %dopar% {
  raw <- read_rds(paste0(pgs.dir, "/", pgs.ls$f[i])) %>%
    mutate(pgs_name = sub(".txt", "", pgs_name))
  corrected <- inner_join(raw, pcs) %>%
    mutate(corrected_pgs = residuals(glm(as.formula(paste0("PGS ~ ", paste(paste0("PC", c(1:20)), collapse = " + "))),
                                         data = inner_join(raw, pcs)))) %>%
    select(IID, PGS, corrected_pgs, pgs_name)
  return(corrected)
}
write_rds(pgs.all, "/Dedicated/jmichaelson-wdata/msmuhammad/scratch/PGS/data/derivatives/all-pgs.rds")
```



### Notes

all data is aligned to hg19

A “Z-score” is a way to normalize data to have an average of 0, and a standard deviation of 1. Meaning a Z-score of -1, would be 1 standard deviation below average. This can easily be converted to a percentile (-1 z-score = 16th percentile, which means that in a room of 100 random people you would score higher than 16 of them).

50th percentile = average, > 50th percentile = above average, < 50th percentile = below average

Polygenic scores calculated using LDPRED2 and regressing out the first 20 genetic PCs 






